Article 1 : 

### 2019-10-07 _posts/2019-09-18-article-1/article-1.Rmd
photo enlevée

---
title: "Article 1 : "
author:
  - name: Aurélie Pinchart
date: 09-18-2019
categories:
  - 
  - 
preview: image/
output:
  distill::distill_article:
    self_contained: false
---

>>>>

---
title: "Article 1 : "
author:
  - name: Aurélie Pinchart
date: 09-18-2019
categories:
  - 
  - 
preview: 
output:
  distill::distill_article:
    self_contained: false
---
